Under-approximation of reachability in multivalued asynchronous networks

### 2013-04-02 main.tex
start cleanup
create appendix
update lfp notation
change title
proofreading of section 2
proofreading of section 3
abstract

\usepackage{prettyref}
\newrefformat{def}{Def.~\ref{#1}}
\newrefformat{fig}{Fig.~\ref{#1}}
%\newrefformat{prop}{Property~\ref{#1}}
\newrefformat{prop}{Proposition~\ref{#1}}
\newrefformat{lem}{Lemma~\ref{#1}}
\newrefformat{th}{Theorem~\ref{#1}}
\newrefformat{co}{Corollary~\ref{#1}}
\newrefformat{sec}{Sect.~\ref{#1}}
\newrefformat{ssec}{Subsect.~\ref{#1}}
\newrefformat{suppl}{Appendix~\ref{#1}}
\newrefformat{eq}{Eq.~\eqref{#1}}
\def\pref{\prettyref}

@@

% Macros
\newcommand{\sN}{\mathbb{N}}
\def\DEF{\stackrel{\Delta}=}
\def\EQDEF{\stackrel{\Delta}\Leftrightarrow}
\newcommand{\segm}[2]{\llbracket #1; #2 \rrbracket}
\def\indexes#1{\mathbb{I}^{#1}}
\newcommand{\sfp}[3]{\mathbf{lfp}\{#1\}\left(#2\mapsto#3\right)}
%\def\lfp{\f{pppf}\;}
\def\f#1{\mathsf{#1}}
\def\prio{\mathsf{prio}}
\newcommand{\bottom}{\perp}
\newcommand{\Vs}{V_\PHs}
\newcommand{\Vh}{V_\PHh}
\newcommand{\Va}{\Vh}
\newcommand{\stable}{\mathsf{stable}}
\newcommand{\update}{\mathsf{update}}
\newcommand{\components}{\Gamma}
\newcommand{\cs}{CS}

\tikzstyle{prio}=[draw,double,-stealth]

@@

@@

% Id est
\newcommand{\ie}{i.e. }

@@

\begin{document}
\begin{frontmatter}
\title{Under-approximation of reachability through static analysis in multivalued asynchronous networks}

@@

To address this issue, we propose an extended definition of the framework, including priority classes for actions.
In this paper, we focus on a restriction of the Process Hitting with two priorities and a specific behaviour of the components, that is sufficient to tackle the aforementioned problem of cooperations.
We show that this class of Process Hitting models allows to represent any asynchronous networks, either boolean or multivalued.
Then we develop a new refinement for the under-approximation of the static analysis to give accurate results for this class of Process Hitting models.
Our method thus allows to efficiently under-approximate local reachability properties in asynchronous multivalued networks.
\end{abstract}
\begin{keyword}
qualitative modelling,
model abstraction,
static analysis,
asynchronous network
\end{keyword}
\end{frontmatter}

@@

%\input{parts/contributions}

>>>>

\usepackage{prettyref}
\newrefformat{def}{Def.~\ref{#1}}
\newrefformat{fig}{Fig.~\ref{#1}}
%\newrefformat{prop}{Property~\ref{#1}}
\newrefformat{prop}{Proposition~\ref{#1}}
\newrefformat{lem}{Lemma~\ref{#1}}
\newrefformat{th}{Theorem~\ref{#1}}
\newrefformat{co}{Corollary~\ref{#1}}
\newrefformat{sec}{Sect.~\ref{#1}}
\newrefformat{ssec}{Subsect.~\ref{#1}}
\newrefformat{suppl}{Appendix~\ref{#1}}
\newrefformat{cr}{Criterion~\ref{#1}}
\newrefformat{eq}{Eq.~\eqref{#1}}
\def\pref{\prettyref}

@@

% Macros
\newcommand{\sN}{\mathbb{N}}
\def\DEF{\stackrel{\Delta}=}
\def\EQDEF{\stackrel{\Delta}\Leftrightarrow}
\newcommand{\segm}[2]{\llbracket #1; #2 \rrbracket}
\def\indexes#1{\mathbb{I}^{#1}}
\def\f#1{\mathsf{#1}}
\def\prio{\mathsf{prio}}
\newcommand{\bottom}{\perp}
\newcommand{\Vs}{V_\PHs}
\newcommand{\Vh}{V_\PHh}
\newcommand{\Va}{\Vh}
\newcommand{\stable}{\mathsf{stable}}
\newcommand{\update}{\mathsf{update}}
\newcommand{\components}{\Gamma}
%\newcommand{\cs}{CS}
\newcommand{\cs}{\Delta}

@@

%\renewcommand{\restriction}[2]{#1_{#2}}

@@

% Id est
\newcommand{\ie}{i.e.~}

@@

\begin{document}
\begin{frontmatter}
\title{Under-approximation of reachability in multivalued asynchronous networks}

@@

To address this issue, we propose an extended definition of the framework, including priority classes for actions.
In this paper, we focus on a restriction of the Process Hitting with two classes of priorities and a specific behaviour of the components, that is sufficient to tackle the aforementioned problem of cooperations.
We show that this class of Process Hitting models allows to represent any Asynchronous Discrete Networks, either Boolean or multivalued.
Then we develop a new refinement for the under-approximation of the static analysis to give accurate results for this class of Process Hitting models.
Our method thus allows to efficiently under-approximate reachability properties in Asynchronous Discrete Networks;
it is in particular conclusive on reachability properties in a 94 components Boolean network, which is unprecedented.
\end{abstract}
\begin{keyword}
qualitative modelling,
model abstraction,
static analysis,
asynchronous network
\end{keyword}
\end{frontmatter}

@@

\input{parts/appendix}
